Publication Bias in the Cochrane Library of Systematic Reviews

### 2019-04-29 Presentation/present.Rnw
Presentation upload

<<echo=FALSE, warning = FALSE, message=FALSE>>= 
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

data = pb.readData(path = PATH_DATA, file = FILE)
tmp = pb.clean(data)
data = tmp[[1]]
aliases = tmp[[2]]

@@

meta <- pb.meta.merge(meta.bin, meta.cont)

@@

barbi2 <- arrange(filter(data, file.nr == 21) %>% 
          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study) %>% group_by(Comparison) %>% distinct(Outcome, .keep_all = T)
barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"

#Missing values
cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
                                 outcome.measure.new == "Hedges' G")

missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
missing.effect <- which(is.na(cont.out$effect))
missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
missing.effects <- length(c(missing.means, wrong.effect))

missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
missing.se <- which(is.na(cont.out$se))
missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
missing.sds <- length(c(missing.sds, wrong.sds))

missing.ss <- which(is.na(data$total1) | is.na(data$total2))
wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
missing.ssize <- length(c(missing.ss, wrong.ss))

missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))

missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
                         "Missing standard deviations and standard errors" = missing.sds,
                         "Missing sample sizes" = missing.ssize,
                         "Missing study year" = missing.year)

#Mean and median number of different outcome types of reviews
mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
  ungroup() %>% group_by(file.nr) %>%
  count() %>% ungroup %>% summarise(mean = mean(n))

median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
  ungroup() %>% group_by(file.nr) %>%
  count() %>% ungroup %>% summarise(mean = median(n))

#Study.year quantiles:
data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
                            quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
                            round(mean(data.ext$study.year, na.rm = T), 2))

#Outcome.measure frequency table:
outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
                                       arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
                                       ungroup() %>% filter(row_number() > 8) %>% 
                                       summarise(outcome.measure.new = "other", n = sum(n)))

outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")

#Total and group size quantiles:
data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
                            quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
                            round(mean(data.ext$total.n, na.rm = T), 2))
treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
                      quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
                      round(mean(data.ext$total1, na.rm = T), 2))

#Frequencies of results:
comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
                      round(mean(comp.freq$n, na.rm = T), 2))

#Frequencies of studies:
study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
                      round(mean(study.freq$n, na.rm = T), 2))

#Pooling studies
cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
  filter(n < 15) %>%
  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
# cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
#   filter(n < 15) %>%
#   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
#                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
#   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)

# cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]

colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
@

@@

\begin{frame}{Cochrane Library Dataset}
% \Sexpr{length(unique(data$file.nr))} systematic reviews with studies published until 2018.
% 
% \Sexpr{length(unique(data$study.name))} studies.
% 
% \Sexpr{dim(data)[1]} study results.
\end{frame}

@@

\begin{frame}{Pooling studies}
Studies of the same outcome, comparison and subgroup can be pooled by meta analyis.

@@

Distort findings of meta-analyses.
\end{frame}

>>>>

<<echo=FALSE, warning = FALSE, warnings = FALSE, message = FALSE>>= 
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

# data = pb.readData(path = PATH_DATA, file = FILE)
# tmp = pb.clean(data)
# data = tmp[[1]]
# aliases = tmp[[2]]

file.dat <- "data.RData"
if (file.exists(file.path(PATH_RESULTS, file.dat))) {
  load(file.path(PATH_RESULTS, file.dat))
} else {
  data = pb.readData(path = PATH_DATA, file = FILE)
	tmp = pb.clean(data)
	data = tmp[[1]]
	aliases = tmp[[2]]
  save(data, file =  file.path(PATH_RESULTS, file.dat))
}

@@

file.meta <- "meta.RData"
if (file.exists(file.path(PATH_RESULTS, file.meta))) {
  load(file.path(PATH_RESULTS, file.meta))
} else {
  meta <- pb.meta.merge(meta.bin, meta.cont)
  save(meta, file =  file.path(PATH_RESULTS, file.meta))
}

# meta <- pb.meta.merge(meta.bin, meta.cont)

@@

barbi2 <- arrange(filter(data, file.nr == 21) %>%
          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study) %>% group_by(Comparison) %>% distinct(Outcome, .keep_all = T)
barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
# 
# #Missing values
# cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
#                                  outcome.measure.new == "Hedges' G") 
# 
# missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
# missing.effect <- which(is.na(cont.out$effect))
# missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
# wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
# missing.effects <- length(c(missing.means, wrong.effect))
# 
# missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
# missing.se <- which(is.na(cont.out$se))
# missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
# wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
# missing.sds <- length(c(missing.sds, wrong.sds))
# 
# missing.ss <- which(is.na(data$total1) | is.na(data$total2))
# wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
# missing.ssize <- length(c(missing.ss, wrong.ss))
# 
# missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
# 
# missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
#                          "Missing standard deviations and standard errors" = missing.sds,
#                          "Missing sample sizes" = missing.ssize,
#                          "Missing study year" = missing.year)
# 
# #Mean and median number of different outcome types of reviews
# mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
#   ungroup() %>% group_by(file.nr) %>%
#   count() %>% ungroup %>% summarise(mean = mean(n))
# 
# median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
#   ungroup() %>% group_by(file.nr) %>%
#   count() %>% ungroup %>% summarise(mean = median(n))
# 
# #Study.year quantiles:
# data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
# publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
#                             quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
#                             round(mean(data.ext$study.year, na.rm = T), 2))
# 
# #Outcome.measure frequency table:
# outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
#                                        arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
#                                      data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
#                                        ungroup() %>% filter(row_number() > 8) %>% 
#                                        summarise(outcome.measure.new = "other", n = sum(n)))
# 
# outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
# names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
# outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
# 
# #Total and group size quantiles:
# data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
# samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
#                             quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
#                             round(mean(data.ext$total.n, na.rm = T), 2))
# treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
#                       quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
#                       round(mean(data.ext$total1, na.rm = T), 2))
# 
# #Frequencies of results:
# comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
# comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
#                       quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
#                       round(mean(comp.freq$n, na.rm = T), 2))
# 
# #Frequencies of studies:
# study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
# study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
#                       quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
#                       round(mean(study.freq$n, na.rm = T), 2))
# 
# #Pooling studies
# cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
#   filter(n < 15) %>%
#   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
#                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
#   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
# # cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
# #   filter(n < 15) %>%
# #   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
# #                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
# #   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
# 
# # cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
# 
# colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")

###################################################################################################################
###################################################################################################################
#Meta-analyses
###################################################################################################################
###################################################################################################################

#Funnel plot example:
biased.rev <- data %>% filter(file.nr == 76 & comparison.nr == 2 & outcome.nr == 2 & subgroup.nr == 4)
meta.example <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, 
												studlab = study.name, sm= "OR", data = biased.rev)

#Publication Bias test plots:
test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                 schwarzer.test = mean(schwarzer.test),
                                                 rucker.test = mean(rucker.test),
                                                 harbord.test = mean(harbord.test),
                                                 peter.test = mean(peter.test))
test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
p.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% 
  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>%  
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
  guides(fill=guide_legend(title=NULL))+
  annotate("text", x = test.bin$test.type, y = 1000, 
           label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
           color = "white")

test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                   begg.test = mean(begg.test),
                                                   thomson.test = mean(thomson.test))
test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
p.cont <- meta.cont %>% ungroup() %>% 
  select(egger.test, thomson.test, begg.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>% 
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL))+
  annotate("text", x = test.cont$test.type, y = 750, 
           label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
           color = "white")

#Significance change after adjustment plot:
change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()

p.fixef.change <- meta %>% ungroup() %>% 
  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change") %>%  
  mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.nonsig", "unchanged.sig", "change.to.sig")) +
  annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
         label = paste(change.fixef[change.fixef$sig.change == 3,]$n, "changed to nonsig."), 
         color = "white")

# Significance after correction plots, separated for meta-analyses with significant publication bias test.
change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>% 
	mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  ggtitle("Meta analysis with non-significant small study effect (peters")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 100, 
           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
           color = "white")

change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% 
	mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  ggtitle("Meta analysis with significant small study effect (peters")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 900, 
           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
           color = "white")

#Publication bias over time and for different sample size:
pbias.time <- meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
  ggplot(aes(x = mean.publication.year, fill = factor(thomson.test), stat(count))) + geom_density(na.rm = T, position = "fill") + 
  guides(fill=guide_legend(title=NULL)) + theme(legend.position = "top") + xlab(label = NULL) +
	scale_fill_discrete(labels= c("Significant", "Not significant"))

pbias.ss <- meta %>% filter(n < 40) %>% ggplot(aes(x = n, fill = factor(thomson.test), stat(count))) + 
  geom_density(position = "fill") + guides(fill=guide_legend(title=NULL)) + xlab(label = NULL) + 
	theme(legend.position = "top") + 
	scale_fill_discrete(labels= c("Significant", "Not significant"))

#Significance proportion plots (before and after correction):
significance <- meta %>% ungroup() %>% 
  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas)  %>% #filter(thomson.test == 1) %>% 
  group_by(significance, estimation.method) %>% count()

p.significance <- meta %>% ungroup() %>% 
  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% #filter(thomson.test == 1) %>% 
  ggplot(aes(x = estimation.method, fill = factor(significance))) + geom_bar() + coord_flip() + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL)) + 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant"))+
  annotate("text", x = significance[significance$significance == 1,]$estimation.method, y = 1500, 
           label = paste(significance[significance$significance == 1,]$n, "significant"), 
           color = "white")

significance <- meta %>% ungroup() %>% 
  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% filter(thomson.test == 1) %>% 
  group_by(significance, estimation.method) %>% count()

p.significance.bias <- meta %>% ungroup() %>% 
  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% filter(thomson.test == 1) %>% 
  ggplot(aes(x = estimation.method, fill = factor(significance))) + geom_bar() + coord_flip() + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL)) + xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant")) +
	ggtitle("Meta analysis with significant small study effect") +
  annotate("text", x = significance[significance$significance == 1,]$estimation.method, y = 250, 
           label = paste(significance[significance$significance == 1,]$n, "significant"), 
           color = "white")

significance <- meta %>% ungroup() %>% 
  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% filter(thomson.test == 0) %>% 
  group_by(significance, estimation.method) %>% count()

p.significance.unbias <- meta %>% ungroup() %>% 
  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% filter(thomson.test == 0) %>% 
  ggplot(aes(x = estimation.method, fill = factor(significance))) + geom_bar() + coord_flip() + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL)) + 
  xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant")) +
	ggtitle("Meta analysis with non-significant small study effect") + 
  annotate("text", x = significance[significance$significance == 1,]$estimation.method, y = 1500, 
           label = paste(significance[significance$significance == 1,]$n, "significant"), 
           color = "white")

#Significance after adjustment separated by significant publication bias tests
change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.bias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 1) %>% mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  ggtitle("Meta analysis with significant small study effect")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 100, 
           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
           color = "white")

change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>% group_by(sig.change, correction.method) %>% count()

p.change.fixef.unbias <- meta %>% 
  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
  filter(thomson.test == 0) %>%   mutate(sig.change = factor(sig.change)) %>% 
  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
  ggtitle("Meta analysis with non-significant small study effect")+ 
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 900, 
           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
           color = "white")

###################################################################################################################
###################################################################################################################
# Results
###################################################################################################################
###################################################################################################################

#Merge comparisons with meta-analysis result:
mly.tomerge <- mly %>% select(meta.id, sig.Q, n.sig.type, n.sig.fishersz, sig.fixef, sig.ranef, sig.ranef.hkn)

data.mly <- merge(x = data.ext, y = mly.tomerge, by = c("meta.id")) #ideally, 278626 comparisons ( = sum(mly$n)), 
# but 300831 (18261 have smaller sample size than mly, but same meta.id)

data.mly <- data.mly %>% filter(total1 > 11 & total2 > 11) #Now 282550

sig.meta.c <- data.mly %>% select(sig.type, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
  gather(key = "meta.analysis.method", value = "sig.meta.analysis") %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))

sig.meta.count.c <- sig.meta.c %>% 
  group_by(sig.meta.analysis, meta.analysis.method) %>% count()

sig.meta.c <- sig.meta.c %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
  geom_bar() + coord_flip() +
  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("meta.nonsig", "meta.sig")) +
  annotate("text", x = sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$meta.analysis.method, y = 100000, 
           label = paste(sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$n, "nonsig."), 
           color = "white")

#Change in significance after meta-analysis, separated by significant effect size estimate
sig.meta <- data.mly %>% 
  select(meta.id, study.id, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
  gather(key = "meta.analysis.method", value = "sig.meta.analysis", sig.fixef:sig.ranef.hkn) %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))

# duplicate.studies <- data.mly %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr, study.name) %>% 
#   count() %>% filter(n > 1) #Merging is not possible for these since studies bear multiple results, but are not distinguishable and are multiplied while merging.

sig.meta.plot <- merge(y = select(data.ext, meta.id, study.id, sig.type), 
                       x = sig.meta, by = c("meta.id", "study.id")) %>% 
  mutate(sig.type = factor(sig.type))

sig.meta.count <- sig.meta.plot %>% 
  group_by(sig.meta.analysis, meta.analysis.method, sig.type) %>% count()

sig.meta.plot1 <- sig.meta.plot %>% filter(sig.type == 1) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
  geom_bar() + coord_flip() + ggtitle("Significant results") + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL)) + 
  xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant")) +
  annotate("text", x = sig.meta.count[which(sig.meta.count$sig.type == 1)[1:3],]$meta.analysis.method, y = 30000, 
           label = paste(sig.meta.count[which(sig.meta.count$sig.type == 1)[1:3],]$n, "changed to nonsig."), 
           color = "white")

nonsig.meta.plot <- sig.meta.plot %>% filter(sig.type == 0) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
  geom_bar() + coord_flip() + ggtitle("Non-significant results") + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL)) + 
  xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant")) +
  annotate("text", x = sig.meta.count[which(sig.meta.count$sig.type == 0)[4:6],]$meta.analysis.method, y = 100000, 
           label = paste(sig.meta.count[which(sig.meta.count$sig.type == 0)[4:6],]$n, "changed to sig."), 
           color = "white")

p.secondary.over.meansig <- mly %>% filter(NA.sig.type != 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
  geom_density(na.rm = T, position = "fill") + 
  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))

@

@@

\begin{frame}{Cochrane Library Dataset}
\Sexpr{length(unique(data$file.nr))} systematic reviews with studies published until 2018.

\Sexpr{length(unique(data$study.name))} studies.

\Sexpr{dim(data)[1]} study results.
\end{frame}

@@

\begin{frame}{Pooling studies - Meta-analysis}
Possible if results have same outcome, comparison and subgroup.

@@

Leads to biased results of meta-analysis.
\end{frame}

\begin{frame}{Publication Bias Tests}
Test for funnel plot asymmetry:

\vspace{-1cm}
\begin{figure}[fragile]
<<echo=FALSE, fig.height = 3, fig.width = 4 >>=
funnel(meta.example)
@
\end{figure}
\end{frame}

\begin{frame}{Publication Bias Tests}
Critical: Number of studies in meta-analysis must be large (>10).

Various tests for meta-analyses with continuous and binary outcomes:

Regression based: Egger's, Peter's or Thompson and Sharp's test

Rank based: Begg and Mazumdar's Test
\end{frame}

\begin{frame}{Publication Bias in Cochrane Library}
Publication bias tests applied for any meta analysis with n > 10

\vspace{-1.7cm}
\begin{figure}[fragile]
<<echo=FALSE, fig.height = 3.1, fig.width = 6.5 >>=
grid.arrange(p.bin, p.cont, ncol = 2)
@
\end{figure}
\end{frame}

\begin{frame}{Publication Bias}
Publication bias variation for time and sample size
\begin{figure}
<<echo=FALSE, fig.height = 3.1, fig.width = 6.5 >>=
grid.arrange(pbias.time, pbias.ss, ncol = 2)
# pbias.time
@
\end{figure}
\end{frame}

\begin{frame}{Publication Bias Adjustment}
Three approaches:

Trim-and-fill: Non-parametric
